{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-11 documents/molecular_dynamics.tex
fuckeradfkljaldkf jaldskfj fuck fuck fuck fuck
pdftex

\paragraph{Molecular dynamics simulation}
\
%\begin{multicols}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%!TeX root = molecular_dynamics
\documentclass[paper.tex]{subfiles}
\begin{document}

\section{Molecular dynamics simulation}
\
%\begin{multicols}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An illustrative - to ensure that there was nothing egregiously wrong with the Stokes drag calculation and to extract various. Certainly this has been done dozens of times in the past. For other reasons to play around with. ]\

\begin{figure}[H]
%	\makebox[\textwidth][c]{
	\centering
	\subfloat[Flower one.]{
	\includegraphics[width=0.4\textwidth]{Vescicle.png}

	}
	\hfill
	\subfloat[The observed spectrum]{
		\includesvg[width=0.4\textwidth]{spectrum}

	}
		\caption{Second.}

\end{figure}

These results are not in any way quantitative, nor do they truly suggest that the effect exists. Lipid vesicle simulations with MARTINI force fields have yielded large-scale stiffness values which are orders of magnitude\cite{Determining2014} from those found experimentally; the speed of sound is also.

A very large amount of tuning and comparison  to obtain any kind of meaningful

Liposome wrapped with BUMPy\cite{BUMPy2018}. \footnote{Durrant's LipidWrapper are equally good options}. MARTINI 
coarse-grained 
lipid and water force field. Run with GROMACS (5?) on the GPU.\footnote{\it "H. H. Williams: Furious activity is no substitute 
	for understanding.".}  A non-equlibrium simulation (very weak thermostat on lipid) with a thick layer of explicit water and then one monolayer of water with restraints (? N/m spring constant) and a strong thermostat () to crudely emulate a large thermal bath (an "open boundary"). This may not be a good way to do this.

molecular dynamics simulation of a lipid vescicle of 30 nm diameter. A mix of POPC and PUPI added to bring liposome charge to 
observed levels.

Rather than use built-in normal-mode methods, Fourier analysis of the (lipid-only) trajectory was performed with TRAVIS\footnote{a 
really fantastic program. Clever user interface too!}, zero-padded at the end to obtain sufficient low-frequency bins with short simulations. The initial "spring Note the non-zero y-intercept.

Computational pipeline available at \ghfile{biology/simulation/GROMACS/BUMPy_bilayer} \footnote{GALAXY or some other, more repeatable "pipeline manager" should have been used}. Elec

Coarse-grained models of COVID with mechanically have recently

\printbibliography{}
